\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{left=0.5in, right=0.5in, top=0.20in, bottom=0.20in}
\usepackage{carlito}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Pamula Rahul - Resume},
    pdfpagemode=FullScreen,
}

% Custom section command optimized for balanced spacing
\newcommand{\resumesection}[1]{%
  \vspace{5pt}%
  \noindent{\large\textbf{#1}}\par
  \vspace{2pt}%
  \hrule height 0.8pt
  \vspace{4pt}%
}

\begin{document}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% Name and Contact Info
{\centering
    {\Huge \textbf{PAMULA RAHUL}}\par
    \vspace{3pt}
    {\small +91 7330864041 \quad ---\quad Maripeda, Mahabubabad, Telangana, India \quad ---\quad Email: \href{mailto:pamularahul123@gmail.com}{pamularahul123@gmail.com}}\par
    \vspace{2pt}
    {\small LinkedIn: \href{http://www.linkedin.com/in/rahul-pamula}{linkedin.com/in/rahul-pamula} \quad ---\quad GitHub: \href{https://github.com/Rahul-pamula}{github.com/Rahul-pamula} \quad ---\quad LeetCode: \href{https://leetcode.com/u/rahulpamula}{leetcode.com/u/rahulpamula}}\par
}

\vspace{3pt}
\hrule height 1.0pt
\vspace{4pt}

% MODIFICATION: Refined grammar and explicitly included "Cloud Computing". Removed repeated adjectives to ensure ATS compliance without fluff.
% Professional Summary
\resumesection{PROFESSIONAL SUMMARY}
\noindent Full Stack Software Developer with hands-on experience building web applications using React.js, FastAPI, Node.js, PostgreSQL, and Cloud Computing platforms including AWS and Microsoft Azure. Experienced in designing RESTful APIs, implementing CI/CD pipelines, containerizing applications with Docker, and deploying production-ready solutions using Agile methodologies.

% MODIFICATION: Removed "KEY ACHIEVEMENTS" section entirely as requested to free up space.

% MODIFICATION: Reordered and strictly formatted Technical Skills to exactly match the provided list. Kept Java.
% Technical Skills
\resumesection{TECHNICAL SKILLS}
\noindent\textbf{Programming Languages:} Java, Python, JavaScript, SQL \\
\noindent\textbf{Frontend:} React.js, Next.js, HTML5, CSS3, Tailwind CSS, Responsive Design \\
\noindent\textbf{Backend:} FastAPI, Node.js, Express.js, RESTful APIs, Authentication \& Authorization, JWT, Microservices, Asynchronous Programming \\
\noindent\textbf{Databases:} PostgreSQL, MongoDB, Redis, Database Design, Database Optimization \\
\noindent\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Microsoft Azure (AZ-900), Docker, GitHub Actions, CI/CD, Containerization, Cloud Deployment \\
\noindent\textbf{Software Engineering:} Data Structures \& Algorithms, Object-Oriented Programming (OOP), Design Patterns, SOLID Principles, SDLC, Agile, Scrum \\
\noindent\textbf{Tools:} Git, GitHub, Postman, VS Code, Linux \\
\noindent\textbf{AI/ML:} Generative AI, NLP

% MODIFICATION: Strengthened action verbs (Designed, Engineered, Optimized, Managed) and avoided repeating "Developed". Integrated required keywords (Agile Sprints, PostgreSQL, API Development, Performance Optimization, Code Reviews, Maintainability).
% Work Experience
\resumesection{WORK EXPERIENCE}

\noindent\textbf{Software Developer} --- ShrFlow \textit{(Collaborated remotely)} \hfill \textbf{Jan 2026 -- Present}
\begin{itemize}[leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt]
    \item Designed a multi-tenant SaaS application leveraging FastAPI and PostgreSQL, implementing asynchronous background processing to improve efficiency.
    \item Engineered full-stack features using React.js, ensuring long-term maintainability through comprehensive code reviews.
    \item Optimized database queries and executed performance optimization strategies, reducing API response time by 35\% and improving application throughput by 40\%.
    \item Managed API development and collaborated in Agile Sprints, actively participating in sprint planning and debugging across the SDLC.
    \item \textbf{Technologies:} React.js \textbullet{} FastAPI \textbullet{} PostgreSQL \textbullet{} Docker \textbullet{} CI/CD \textbullet{} Git \textbullet{} GitHub
\end{itemize}

\vspace{4pt}

% MODIFICATION: Replaced 'Cloud Deployment' with 'Vercel' since the link uses vercel.app. Changed starting verb to 'Built' and 'Executed'.
\noindent\textbf{Freelance Full Stack Developer} --- Tailoring Platform \textit{|\ \href{https://github.com/Rahul-pamula}{GitHub} \ | \ \href{https://tailoring-red.vercel.app}{Live Demo}} \hfill \textbf{Jan 2026}
\begin{itemize}[leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt]
    \item Built and deployed a responsive React.js web application with an admin dashboard for order and pricing management, driving a 30\% increase in business order volume.
    \item Executed extensive manual and automated UI testing to guarantee a consistent cross-device user experience.
    \item \textbf{Technologies:} React.js \textbullet{} HTML5 \textbullet{} CSS3 \textbullet{} Vercel \textbullet{} Responsive Design
\end{itemize}

% Projects
\resumesection{KEY PROJECTS}

% MODIFICATION: Used varied verbs (Architected, Created, Implemented, Configured). Ensured requested technologies are present in the list (Supabase, FastAPI, React.js, GitHub Actions, REST APIs, Authentication, CI/CD).
\noindent\textbf{Email\_To\_Telebot} --- Serverless Cloud Architecture \textit{|\ \href{https://github.com/Rahul-pamula/Email_to_telebot}{GitHub} \ | \ \href{https://rahul-pamula.github.io/Email_to_telebot/}{Live Demo}} \hfill \textbf{June 2026 -- Present}
\begin{itemize}[leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt]
    \item Architected a serverless backend using Supabase Edge Functions and Telegram Webhooks.
    \item Created RESTful APIs for automated email processing and inbox summarization.
    \item Implemented RBAC and secure API management using Supabase Authentication and Vault.
    \item Configured automated deployment pipelines using GitHub Actions for continuous integration.
    \item \textbf{Technologies:} React.js \textbullet{} FastAPI \textbullet{} Supabase \textbullet{} REST APIs \textbullet{} Authentication \textbullet{} GitHub Actions \textbullet{} CI/CD
\end{itemize}

\vspace{4pt}

% MODIFICATION: Used varied verbs (Developed, Programmed, Engineered, Designed). Integrated "Weather API Integration", "MongoDB", "Responsive Dashboard", and "RESTful APIs" directly into the bullet points.
\noindent\textbf{AgriFlow} --- Full-Stack AI Platform \textit{|\ \href{https://github.com/Rahul-pamula/AgriFlow}{GitHub} \ | \ \href{https://agriflow-frontend.onrender.com/}{Live Demo}} \hfill \textbf{2026}
\begin{itemize}[leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt]
    \item Developed a full-stack MERN application providing real-time data insights and agricultural recommendations.
    \item Programmed RESTful APIs and facilitated seamless Weather API integration for accurate forecasting.
    \item Engineered advanced search functionality for unstructured data using MongoDB.
    \item Designed a responsive dashboard to visualize real-time agricultural insights effectively.
    \item \textbf{Technologies:} React.js \textbullet{} Node.js \textbullet{} Express.js \textbullet{} MongoDB \textbullet{} RESTful APIs \textbullet{} JSON
\end{itemize}

\vspace{4pt}

% MODIFICATION: Used exact requested string "Integrated Azure AI services for NLP-based deadline extraction.". Varied starting verbs (Constructed, Developed, Integrated, Established).
\noindent\textbf{Chatnalyxer} --- AI Productivity App \textit{|\ \href{https://github.com/Rahul-pamula/chatnalyxer.git}{GitHub} \ | \ \href{http://chatnalyxer.app/}{Live Demo}} \hfill \textbf{Aug 2025 -- Oct 2025}
\begin{itemize}[leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt]
    \item Constructed a cross-platform application integrated with a robust Node.js and PostgreSQL backend.
    \item Developed secure REST APIs utilizing JWT for robust Authentication \& Authorization.
    \item Integrated Azure AI services for NLP-based deadline extraction and automated data entry.
    \item Established CI/CD pipelines using GitHub Actions to streamline Cloud Deployment.
    \item \textbf{Technologies:} React Native \textbullet{} Node.js \textbullet{} PostgreSQL \textbullet{} Docker \textbullet{} JWT \textbullet{} GitHub Actions \textbullet{} CI/CD
\end{itemize}

% Education
\resumesection{EDUCATION}

\noindent\textbf{Bachelor of Technology in Computer Science and Engineering (AI \& ML)} \hfill \textbf{June 2023 -- Present} \\
% MODIFICATION: Replaced "Pre-final Year" with "Expected Graduation: 2027" while keeping CGPA.
\textit{Parul University, Gujarat, India \ | \ Expected Graduation: 2027 \ | \ CGPA: 8.12/10.0}

\vspace{4pt}

\noindent\textbf{Class XII (82.6\%) \& Class X (9.7/10.0 CGPA)} --- Telangana State Board \hfill \textbf{2021 -- 2023}

% Certifications
\resumesection{CERTIFICATIONS}

\noindent\textbf{Microsoft Certified: Azure Fundamentals (AZ-900)} --- Microsoft \hfill \textbf{2025} \textit{(\href{https://www.credly.com/badges/cb01588f-556d-448d-84f3-aebeef100485/public_url}{Credly Badge})} \\
\noindent\textbf{Introduction to SQL} --- DataFlair \hfill \textbf{2025} \textit{(\href{https://drive.google.com/file/d/1oosWCwBwj4BE8eseplqIj-2Cx2dp42X3/view?usp=sharing}{Certificate})} \\
\noindent\textbf{AI/ML Sprint} --- ByteXL \hfill \textbf{2025} \textit{(\href{https://drive.google.com/file/d/1Didyx_p9tVhQ_uAG6CP7Sf4VfBXdAbES/view?usp=sharing}{Certificate})}

\end{document}
